noam_final_analyses

### 2024-09-10 noam_final_analyses.Rmd
up to current analyses

alpha_diversity_quad_macro <- full_join(alpha_diversity_quad_macro, quad_macro_betadisper[,c("year", "betadispersion_trans", "location")], by = c("location", "year"))
```

>>>>

alpha_diversity_quad_macro <- full_join(alpha_diversity_quad_macro, quad_macro_betadisper[,c("year", "betadispersion_trans", "location")], by = c("location", "year"))

fringing_all_quad <- na.omit(subset(alpha_diversity_quad, habitat == "fringing"))
backreef_all_quad <- na.omit(subset(alpha_diversity_quad, habitat == "backreef"))
outer10_all_quad <- subset(alpha_diversity_quad, habitat == "outer_10") 
outer10_all_quad <- outer10_all_quad[,-which(names(outer10_all_quad) %in% c("mean_n", "n_cv"))]
outer10_all_quad <- na.omit(outer10_all_quad)
outer17_all_quad <- subset(alpha_diversity_quad, habitat == "outer_17") 
outer17_all_quad <- outer17_all_quad[,-which(names(outer17_all_quad) %in% c("mean_n", "n_cv", "herbivore_biomass", "herbivore_evenness", "herbivore_richness", "herbivore_shannon"))]
outer17_all_quad <- na.omit(outer17_all_quad)

fringing_macro_quad <- na.omit(subset(alpha_diversity_quad_macro, habitat == "fringing"))
backreef_macro_quad <- na.omit(subset(alpha_diversity_quad_macro, habitat == "backreef"))
outer10_macro_quad <- subset(alpha_diversity_quad, habitat == "outer_10") 
outer10_macro_quad <- outer10_macro_quad[,-which(names(outer10_macro_quad) %in% c("mean_n", "n_cv"))]
outer10_macro_quad <- na.omit(outer10_macro_quad)
outer17_macro_quad <- subset(alpha_diversity_quad, habitat == "outer_17") 
outer17_macro_quad <- outer17_macro_quad[,-which(names(outer17_macro_quad) %in% c("mean_n", "n_cv", "herbivore_biomass", "herbivore_evenness", "herbivore_richness", "herbivore_shannon"))]
outer17_macro_quad <- na.omit(outer17_macro_quad)
```

```{r stepwise model all shannon quad}
fringing_all_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year + mean_n +  mean_temp_c +  herbivore_evenness + (1|site/location), data = fringing_all_quad, na.action = na.pass)
fringing_all_shannon_dredge <- dredge(fringing_all_shannon_mod_universal) 
model.sel(fringing_all_shannon_dredge) # all terms
qqnorm(residuals(fringing_all_shannon_mod_universal))# a little wonky
qqline(residuals(fringing_all_shannon_mod_universal))
plot(residuals(fringing_all_shannon_mod_universal) ~ fitted(fringing_all_shannon_mod_universal)) # sharp line again
summary(fringing_all_shannon_mod_universal)
Anova(fringing_all_shannon_mod_universal) # only year and mean temp sig. herbivore evenness is borderline.

fringing_emm <-as.data.frame(emmeans(fringing_all_shannon_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(fringing_all_quad$mean_temp_c),
                                                            max(fringing_all_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = fringing_all_quad, aes(x = mean_temp_c, y = shannon))+
  geom_line(data = fringing_emm, aes(x = mean_temp_c, y = emmean)) +
  geom_ribbon(data = fringing_emm, aes(x = mean_temp_c, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Mean Temp (C)", y = "Fringing Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

backreef_all_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year  + wave_power_adcp + mean_n + mean_temp_c +  herbivore_evenness + (1|site/location), data = backreef_all_quad, na.action = na.pass)
backreef_all_shannon_dredge <- dredge(backreef_all_shannon_mod_universal) # some have convergence issues
model.sel(backreef_all_shannon_dredge) #  best includes all but results in only NaN results. Next best removes year and wave power
backreef_all_shannon_top_mod <- glmmTMB(log(shannon + 1) ~ mean_n + mean_temp_c +  herbivore_evenness + (1|site/location), data = backreef_all_quad, na.action = na.pass) #  a little wonky on the tail but not bad
hist(residuals(backreef_all_shannon_top_mod)) # still a little chunky
plot(residuals(backreef_all_shannon_top_mod) ~ fitted(backreef_all_shannon_top_mod)) # same stripe
summary(backreef_all_shannon_top_mod)
Anova(backreef_all_shannon_top_mod)

backreef_emm <-as.data.frame(emmeans(backreef_all_shannon_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(backreef_all_quad$mean_temp_c),
                                                            max(backreef_all_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = backreef_all_quad, aes(x = mean_temp_c, y = shannon))+
  geom_line(data = backreef_emm, aes(x = mean_temp_c, y = emmean)) +
  geom_ribbon(data = backreef_emm, aes(x = mean_temp_c, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Mean Temp (C)", y = "Backreef Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

backreef_emm_2 <-as.data.frame(emmeans(backreef_all_shannon_top_mod, ~mean_n,
                                     at = list(mean_n = seq(min(backreef_all_quad$mean_n),
                                                            max(backreef_all_quad$mean_n),
                                                            0.01)))) 
ggplot()+
  geom_point(data = backreef_all_quad, aes(x = mean_n, y = shannon))+
  geom_line(data = backreef_emm_2, aes(x = mean_n, y = emmean)) +
  geom_ribbon(data = backreef_emm_2, aes(x = mean_n, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Mean N", y = "Backreef Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

backreef_emm_3 <-as.data.frame(emmeans(backreef_all_shannon_top_mod, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(backreef_all_quad$herbivore_evenness),
                                                            max(backreef_all_quad$herbivore_evenness),
                                                            0.01)))) 
ggplot()+
  geom_point(data = backreef_all_quad, aes(x = herbivore_evenness, y = shannon))+
  geom_line(data = backreef_emm_3, aes(x = herbivore_evenness, y = emmean)) +
  geom_ribbon(data = backreef_emm_3, aes(x = herbivore_evenness, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Herbivore evenness", y = "Backreef Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

# Outer10
outer10_all_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year  + wave_power_adcp  + mean_temp_c +  herbivore_evenness + (1|site/location), data = outer10_all_quad, na.action = na.pass)
outer10_all_shannon_dredge <- dredge(outer10_all_shannon_mod_universal) 
model.sel(outer10_all_shannon_dredge) #  best includes just herbivore evenness 
outer10_all_shannon_top_mod <- glmmTMB(log(shannon + 1) ~  herbivore_evenness + (1|site/location), data = outer10_all_quad, na.action = na.pass)
qqnorm(residuals(outer10_all_shannon_top_mod)) # slight negative skew
plot(residuals(outer10_all_shannon_top_mod) ~ fitted(outer10_all_shannon_top_mod)) # looks fine
summary(outer10_all_shannon_top_mod)
Anova(outer10_all_shannon_top_mod)
outer10_emm <-as.data.frame(emmeans(outer10_all_shannon_top_mod, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(outer10_all_quad$herbivore_evenness),
                                                            max(outer10_all_quad$herbivore_evenness),
                                                            0.05))))

ggplot()+
  geom_point(data = outer10_all_quad, aes(x = herbivore_evenness, y = shannon))+
  geom_line(data = outer10_emm, aes(x = herbivore_evenness, y = emmean)) +
  geom_ribbon(data = outer10_emm, aes(x = herbivore_evenness, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Herbivore evenness", y = "Outer 10 Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

## outer17

outer17_all_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year  + wave_power_adcp  + mean_temp_c + (1|site/location), data = outer17_all_quad, na.action = na.pass)
outer17_all_shannon_dredge <- dredge(outer17_all_shannon_mod_universal) 
model.sel(outer17_all_shannon_dredge) # best includes all but results in NaNs
# next best includes just year and mean_temp
outer17_all_shannon_top_mod <- glmmTMB(log(shannon + 1) ~ year  + mean_temp_c + (1|site/location), data = outer17_all_quad, na.action = na.pass)
hist(residuals(outer17_all_shannon_top_mod))
plot(residuals(outer17_all_shannon_top_mod) ~ fitted(outer17_all_shannon_top_mod)) # looks fine
summary(outer17_all_shannon_top_mod)
Anova(outer17_all_shannon_top_mod)

outer17_emm <-as.data.frame(emmeans(outer17_all_shannon_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(outer17_all_quad$mean_temp_c),
                                                            max(outer17_all_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = outer17_all_quad, aes(x = mean_temp_c, y = shannon))+
  geom_line(data = outer17_emm, aes(x = mean_temp_c, y = emmean)) +
  geom_ribbon(data = outer17_emm, aes(x = mean_temp_c, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Mean Temp (C)", y = "Outer 17 Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

```
```{r stepwise model all betadisp quad}
fringing_all_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year + mean_n +  mean_temp_c +  herbivore_evenness + (1|site/location), data = fringing_all_quad, na.action = na.pass, family = beta_family())
fringing_all_betadisp_dredge <- dredge(fringing_all_betadisp_mod_universal) 
model.sel(fringing_all_betadisp_dredge) # best includes evenness, nitrogen, and year
fringing_all_betadisp_top_mod <- glmmTMB(betadispersion_trans ~ year +  mean_n +  herbivore_evenness + (1|site/location), data = fringing_all_quad, na.action = na.pass, family = beta_family())
hist(residuals(fringing_all_betadisp_top_mod)) #  positive skew
plot(residuals(fringing_all_betadisp_top_mod) ~ fitted(fringing_all_betadisp_top_mod)) # negative trend
summary(fringing_all_betadisp_top_mod)
Anova(fringing_all_betadisp_top_mod) # herbivore evenness not sig

fringing_betadisp_emm <-as.data.frame(emmeans(fringing_all_betadisp_top_mod, ~mean_n,
                                     at = list(mean_n = seq(min(fringing_all_quad$mean_n),
                                                            max(fringing_all_quad$mean_n),
                                                            0.01)))) 
ggplot()+
  geom_point(data = fringing_all_quad, aes(x = mean_n, y = betadispersion_trans))+
  geom_line(data = fringing_betadisp_emm, aes(x = mean_n, y = inv_logit(emmean))) +
  geom_ribbon(data = fringing_betadisp_emm, aes(x = mean_n, ymin = inv_logit(asymp.LCL),
                                                ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Mean N", y = "Fringing Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

backreef_all_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year  + wave_power_adcp + mean_n + mean_temp_c +  herbivore_evenness + (1|site/location), data = backreef_all_quad, na.action = na.pass, family = beta_family())
backreef_all_betadisp_dredge <- dredge(backreef_all_betadisp_mod_universal) # most have convergence issues
model.sel(backreef_all_betadisp_dredge) #  best includes evenness nitrogen year
backreef_all_betadisp_top_mod <- glmmTMB(betadispersion_trans ~ year  +  mean_n + herbivore_evenness + (1|site/location), data = backreef_all_quad, na.action = na.pass, family = beta_family()) 
hist(residuals(backreef_all_betadisp_top_mod)) # positive skew
plot(residuals(backreef_all_betadisp_top_mod) ~ fitted(backreef_all_betadisp_top_mod)) # negative trend
summary(backreef_all_betadisp_top_mod)
Anova(backreef_all_betadisp_top_mod) # evenness and year sig

backreef_betadisp_emm <-as.data.frame(emmeans(backreef_all_betadisp_top_mod, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(backreef_all_quad$herbivore_evenness),
                                                            max(backreef_all_quad$herbivore_evenness),
                                                            0.01)))) 
ggplot()+
  geom_point(data = backreef_all_quad, aes(x = herbivore_evenness, y = betadispersion_trans))+
  geom_line(data = backreef_betadisp_emm, aes(x = herbivore_evenness, y = inv_logit(emmean))) +
  geom_ribbon(data = backreef_betadisp_emm, aes(x = herbivore_evenness, ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Herbivore evenness", y = "Backreef Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

# Outer10
outer10_all_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year  + wave_power_adcp  + mean_temp_c +  herbivore_evenness + (1|site/location), data = outer10_all_quad, na.action = na.pass, family = beta_family()) # model convergence
outer10_all_betadisp_dredge <- dredge(outer10_all_betadisp_mod_universal) # all have errors of some kind
model.sel(outer10_all_betadisp_dredge) #  best includes herbivore evenness, temp, and year
outer10_all_betadisp_top_mod <- glmmTMB(betadispersion_trans ~ year + mean_temp_c +  herbivore_evenness + (1|site/location), data = outer10_all_quad, na.action = na.pass, family = beta_family()) 
qqnorm(residuals(outer10_all_betadisp_top_mod)) # positive skew
plot(residuals(outer10_all_betadisp_top_mod) ~ fitted(outer10_all_betadisp_top_mod)) # less negative than before
summary(outer10_all_betadisp_top_mod)
Anova(outer10_all_betadisp_top_mod) # all sig
outer10_betadisp_emm <-as.data.frame(emmeans(outer10_all_betadisp_top_mod, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(outer10_all_quad$herbivore_evenness),
                                                            max(outer10_all_quad$herbivore_evenness),
                                                            0.05))))

ggplot()+
  geom_point(data = outer10_all_quad, aes(x = herbivore_evenness, y = betadispersion_trans))+
  geom_line(data = outer10_betadisp_emm, aes(x = herbivore_evenness, y = inv_logit(emmean))) +
  geom_ribbon(data = outer10_betadisp_emm,
              aes(x = herbivore_evenness, ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Herbivore evenness", y = "Outer 10 Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

outer10_betadisp_emm2 <-as.data.frame(emmeans(outer10_all_betadisp_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(outer10_all_quad$mean_temp_c),
                                                            max(outer10_all_quad$mean_temp_c),
                                                            0.05))))

ggplot()+
  geom_point(data = outer10_all_quad, aes(x = mean_temp_c, y = betadispersion_trans))+
  geom_line(data = outer10_betadisp_emm2, aes(x = mean_temp_c, y = inv_logit(emmean))) +
  geom_ribbon(data = outer10_betadisp_emm2,
              aes(x = mean_temp_c, ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Mean temp (C)", y = "Outer 10 Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

## outer17

outer17_all_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year  + wave_power_adcp  + mean_temp_c + (1|site/location), data = outer17_all_quad, na.action = na.pass, family = beta_family()) # convergence issue
outer17_all_betadisp_dredge <- dredge(outer17_all_betadisp_mod_universal) 
model.sel(outer17_all_betadisp_dredge) # best mean temp and year
outer17_all_betadisp_top_mod <-  glmmTMB(betadispersion_trans ~ year  +  mean_temp_c + (1|site/location), data = outer17_all_quad, na.action = na.pass, family = beta_family())
hist(residuals(outer17_all_betadisp_top_mod)) # similar issues
plot(residuals(outer17_all_betadisp_top_mod) ~ fitted(outer17_all_betadisp_top_mod)) # similar issues
summary(outer17_all_betadisp_top_mod)
Anova(outer17_all_betadisp_top_mod) # sig

outer17_betadisp_emm <-as.data.frame(emmeans(outer17_all_betadisp_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(outer17_all_quad$mean_temp_c),
                                                            max(outer17_all_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = outer17_all_quad, aes(x = mean_temp_c, y = betadispersion_trans))+
  geom_line(data = outer17_betadisp_emm, aes(x = mean_temp_c, y = inv_logit(emmean))) +
  geom_ribbon(data = outer17_betadisp_emm, aes(x = mean_temp_c, ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Mean Temp (C)", y = "Outer 17 beta dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

```{r stepwise model macro shannon quad}
fringing_macro_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year + mean_n +  mean_temp_c +  herbivore_evenness + (1|site/location), data = fringing_macro_quad, na.action = na.pass)
fringing_macro_shannon_dredge <- dredge(fringing_macro_shannon_mod_universal) 
model.sel(fringing_macro_shannon_dredge) # best just year
fringing_macro_shannon_top_mod <- glmmTMB(log(shannon + 1) ~ year + (1|site/location), data = fringing_macro_quad, na.action = na.pass)
hist(residuals(fringing_macro_shannon_top_mod))# almost bimodal

plot(residuals(fringing_macro_shannon_top_mod) ~ fitted(fringing_macro_shannon_top_mod)) # sharp line again
summary(fringing_macro_shannon_top_mod)
Anova(fringing_macro_shannon_top_mod)

## Backreef - includes macro

backreef_macro_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year  + wave_power_adcp + mean_n + mean_temp_c +  herbivore_evenness + (1|site/location), data = backreef_macro_quad, na.action = na.pass)
backreef_macro_shannon_dredge <- dredge(backreef_macro_shannon_mod_universal) # some have convergence issues
model.sel(backreef_macro_shannon_dredge) #  best  removes wave power
backreef_macro_shannon_top_mod <- glmmTMB(log(shannon + 1) ~ year + mean_n + mean_temp_c +  herbivore_evenness + (1|site/location), data = backreef_macro_quad, na.action = na.pass) #  a little wonky on the tail but not bad
hist(residuals(backreef_macro_shannon_top_mod)) # bimodal again... zero inflation?
plot(residuals(backreef_macro_shannon_top_mod) ~ fitted(backreef_macro_shannon_top_mod)) # same stripe
summary(backreef_macro_shannon_top_mod)
Anova(backreef_macro_shannon_top_mod) # just year and temp sig

backreef_emm <-as.data.frame(emmeans(backreef_macro_shannon_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(backreef_macro_quad$mean_temp_c),
                                                            max(backreef_macro_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = backreef_macro_quad, aes(x = mean_temp_c, y = shannon))+
  geom_line(data = backreef_emm, aes(x = mean_temp_c, y = emmean)) +
  geom_ribbon(data = backreef_emm, aes(x = mean_temp_c, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Mean Temp (C)", y = "Backreef Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

# Outer10
outer10_macro_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year  + wave_power_adcp  + mean_temp_c +  herbivore_evenness + (1|site/location), data = outer10_macro_quad, na.action = na.pass)
outer10_macro_shannon_dredge <- dredge(outer10_macro_shannon_mod_universal) 
model.sel(outer10_macro_shannon_dredge) #  best includes just herbivore evenness 
outer10_macro_shannon_top_mod <- glmmTMB(log(shannon + 1) ~  herbivore_evenness + (1|site/location), data = outer10_macro_quad, na.action = na.pass)
hist(residuals(outer10_macro_shannon_top_mod)) # slight negative skew but better than the others
plot(residuals(outer10_macro_shannon_top_mod) ~ fitted(outer10_macro_shannon_top_mod)) # looks fine
summary(outer10_macro_shannon_top_mod)
Anova(outer10_macro_shannon_top_mod)
outer10_emm <-as.data.frame(emmeans(outer10_macro_shannon_top_mod, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(outer10_macro_quad$herbivore_evenness),
                                                            max(outer10_macro_quad$herbivore_evenness),
                                                            0.05))))

ggplot()+
  geom_point(data = outer10_macro_quad, aes(x = herbivore_evenness, y = shannon))+
  geom_line(data = outer10_emm, aes(x = herbivore_evenness, y = emmean)) +
  geom_ribbon(data = outer10_emm, aes(x = herbivore_evenness, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Herbivore evenness", y = "Outer 10 Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

## outer17

outer17_macro_shannon_mod_universal <- glmmTMB(log(shannon + 1) ~ year  + wave_power_adcp  + mean_temp_c + (1|site/location), data = outer17_macro_quad, na.action = na.pass)
outer17_macro_shannon_dredge <- dredge(outer17_macro_shannon_mod_universal) 
model.sel(outer17_macro_shannon_dredge) # best includes all but results in NaNs
# next best includes just year and mean_temp
outer17_macro_shannon_top_mod <- glmmTMB(log(shannon + 1) ~ year  + mean_temp_c + (1|site/location), data = outer17_macro_quad, na.action = na.pass)
hist(residuals(outer17_macro_shannon_top_mod)) # negative skew
plot(residuals(outer17_macro_shannon_top_mod) ~ fitted(outer17_macro_shannon_top_mod)) # looks fine
summary(outer17_macro_shannon_top_mod)
Anova(outer17_macro_shannon_top_mod)

outer17_emm <-as.data.frame(emmeans(outer17_macro_shannon_top_mod, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(outer17_macro_quad$mean_temp_c),
                                                            max(outer17_macro_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = outer17_macro_quad, aes(x = mean_temp_c, y = shannon))+
  geom_line(data = outer17_emm, aes(x = mean_temp_c, y = emmean)) +
  geom_ribbon(data = outer17_emm, aes(x = mean_temp_c, ymin = lower.CL, ymax = upper.CL, alpha = 0.2), show.legend = F) +
  scale_y_log10() + 
  labs(x = "Mean Temp (C)", y = "Outer 17 Shannon Index (H')") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

```
```{r stepwise model macro betadisp quad}
fringing_macro_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year + mean_n +  mean_temp_c +  herbivore_evenness + (1|site/location), data = fringing_macro_quad, na.action = na.pass, family = beta_family())
fringing_macro_betadisp_dredge <- dredge(fringing_macro_betadisp_mod_universal) 
model.sel(fringing_macro_betadisp_dredge) # best includes all
hist(residuals(fringing_macro_betadisp_mod_universal)) #  a little lumpy but not bad
plot(residuals(fringing_macro_betadisp_mod_universal) ~ fitted(fringing_macro_betadisp_mod_universal)) # negative trend
summary(fringing_macro_betadisp_mod_universal)
Anova(fringing_macro_betadisp_mod_universal) # all sig

fringing_betadisp_emm <-as.data.frame(emmeans(fringing_macro_betadisp_mod_universal, ~mean_n,
                                     at = list(mean_n = seq(min(fringing_macro_quad$mean_n),
                                                            max(fringing_macro_quad$mean_n),
                                                            0.01)))) 
ggplot()+
  geom_point(data = fringing_macro_quad, aes(x = mean_n, y = betadispersion_trans))+
  geom_line(data = fringing_betadisp_emm, aes(x = mean_n, y = inv_logit(emmean))) +
  geom_ribbon(data = fringing_betadisp_emm, aes(x = mean_n, ymin = inv_logit(asymp.LCL),
                                                ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Mean N", y = "Fringing Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

fringing_betadisp_emm2 <-as.data.frame(emmeans(fringing_macro_betadisp_mod_universal, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(fringing_macro_quad$herbivore_evenness),
                                                            max(fringing_macro_quad$herbivore_evenness),
                                                            0.01)))) 
ggplot()+
  geom_point(data = fringing_macro_quad, aes(x = herbivore_evenness, y = betadispersion_trans))+
  geom_line(data = fringing_betadisp_emm2, aes(x = herbivore_evenness, y = inv_logit(emmean))) +
  geom_ribbon(data = fringing_betadisp_emm2, aes(x = herbivore_evenness, ymin = inv_logit(asymp.LCL),
                                                ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Herbivore evenness", y = "Fringing Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

fringing_betadisp_emm3 <-as.data.frame(emmeans(fringing_macro_betadisp_mod_universal, ~mean_temp_c,
                                     at = list(mean_temp_c = seq(min(fringing_macro_quad$mean_temp_c),
                                                            max(fringing_macro_quad$mean_temp_c),
                                                            0.01)))) 
ggplot()+
  geom_point(data = fringing_macro_quad, aes(x = mean_temp_c, y = betadispersion_trans))+
  geom_line(data = fringing_betadisp_emm3, aes(x = mean_temp_c, y = inv_logit(emmean))) +
  geom_ribbon(data = fringing_betadisp_emm3, aes(x = mean_temp_c, ymin = inv_logit(asymp.LCL),
                                                ymax = inv_logit(asymp.UCL), alpha = 0.2), show.legend = F) +
  labs(x = "Mean Temp (C)", y = "Fringing Beta Dispersion") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

## Backreef - includes macro

backreef_macro_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year  + wave_power_adcp + mean_n + mean_temp_c +  herbivore_evenness + (1|site/location), data = backreef_macro_quad, na.action = na.pass, family = beta_family())
backreef_macro_betadisp_dredge <- dredge(backreef_macro_betadisp_mod_universal) # most have convergence issues
model.sel(backreef_macro_betadisp_dredge) #  best includes nitrogen and year
backreef_macro_betadisp_top_mod <- glmmTMB(betadispersion_trans ~ year  +  mean_n  + (1|site/location), data = backreef_macro_quad, na.action = na.pass, family = beta_family()) 
hist(residuals(backreef_macro_betadisp_top_mod)) # not bad
plot(residuals(backreef_macro_betadisp_top_mod) ~ fitted(backreef_macro_betadisp_top_mod)) # weird cluster, slight negative trend
summary(backreef_macro_betadisp_top_mod)
Anova(backreef_macro_betadisp_top_mod)

# Outer10
outer10_macro_betadisp_mod_universal <- glmmTMB(betadispersion_trans ~ year  + wave_power_adcp  + mean_temp_c +  herbivore_evenness + (1|site/location), data = outer10_macro_quad, na.action = na.pass, family = beta_family()) # model convergence
outer10_macro_betadisp_dredge <- dredge(outer10_macro_betadisp_mod_universal) # all have errors of some kind
model.sel(outer10_macro_betadisp_dredge) #  best includes herbivore evenness, temp, and year
outer10_macro_betadisp_top_mod <- glmmTMB(betadispersion_trans ~ year + mean_temp_c +  herbivore_evenness + (1|site/location), data = outer10_macro_quad, na.action = na.pass, family = beta_family()) 
qqnorm(residuals(outer10_macro_betadisp_top_mod)) # positive skew
plot(residuals(outer10_macro_betadisp_top_mod) ~ fitted(outer10_macro_betadisp_top_mod)) # less negative than before
summary(outer10_macro_betadisp_top_mod)
Anova(outer10_macro_betadisp_top_mod) # all sig
outer10_betadisp_emm <-as.data.frame(emmeans(outer10_macro_betadisp_top_mod, ~herbivore_evenness,
                                     at = list(herbivore_evenness = seq(min(outer10_macro_quad$herbivore_evenness),
                                                            max(outer10_macro_quad$herbivore_evenness),
                                                            0.05))))
